---
title: "Untitled"
author: "Roopa,  Uros"
date: "October 29, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
Load the dataset in R and create a new column called 'rDate' convert the 'date'
column into the 'date' datatype.

```{r}
install.packages("anytime")
library("anytime")
library("zoo")
dataBay<-read.csv("C:\\Users\\Uros Randelovic\\Documents\\R workspace\\BUS 111\\Ebay\\data.csv")

dataBay$rDate <- as.Date(data$date, format="%m/%d/%Y")

View(dataBay)

```
b) Determine the date that started the treatment period. That is, write code to determine
the earliest date in the treatment period. 


```{r}

treatedPeriod <- dataBay[which(dataBay$isTreatmentPeriod==0),]
untreatedPeriod <-dataBay[which(dataBay$isTreatmentPeriod==1),]

#earliest date
min(treatedPeriod$rDate)

```
How were the treatment and control groups treated differently during this period? 5%
- Treatment group was shown ads in the time indicated and the control group was not shown ads. 




c) The data contains a control group, which are shown search ads throughout the data,
and a treatment group, which are only shown search ads before the treatment period.i. Run a regression that compares log(revenue) of the treatment group in the
pre-treatment period and in the treatment period. 5%

```{r}

summary((lm(log(dataBay$revenue) ~ dataBay$isTreatmentPeriod+dataBay$isTreatmentGroup)))



```

ii. What do the resulting coefficient estimates say about the effectiveness of
advertising? Be as specific as you can. 10%





d) Now we will use the control group for a true experimental approach. First, we will
check the randomization was done properly.

i. Run a regression that compares log(revenue) of the treatment group and the
control group in the pre-treatment period. 10%

```{r}

summary(lm(log(dataBay$revenue) ~ dataBay$isTreatmentGroup + dataBay$isTreatmentPeriod + (dataBay$isTreatmentPeriod*dataBay$isTreatmentGroup)))




```



ii. What is the purpose of this randomization check? What do the results of this
regression show? 5%





e) Now, using the post treatment data, determine the effectiveness of eBay ads.

i. Run a regression with log(revenue) as the dependent variable, and whether
the DMA is in the treatment group as the independent variable. 10%
```{r}
options(max.print=999999)
summary(lm(log(dataBay$revenue)~(dataBay$dma)))


```

ii. What do the resulting coefficient estimates say about the effectiveness of
advertising? Be as specific as you can. 10%

iii. What was the purpose of the control group here? What factor was
unaccounted for in part c, but was accounted for in part e? 10%

iv. Does this R-squared of this regression affect the interpretation or confidence in
the estimate of the effectiveness of advertising? 10%

f) Check whether the effectiveness of eBay advertising changes over time. Create a
new variable called month, which contains a factor variable of the month that the date
falls in. In a new regression on the post treatment data, interact whether the DMA is in
the treatment group with this month variable. Paste a summary of this regression into
your pdf. 10%
Hint: Creating the month variable can be done in a least two ways. One method
would use the paste and the substr function. Another would use the lubridate
package. Any approach that works is acceptable.
```{r}
library(lubridate)
dataBay$dateM <- month(dataBay$rDate)
View(dataBay)

summary(lm(dataBay$dma~factor(dataBay$dateM)))

```


g) Throughout the analysis regression were run on log(revenue) rather than revenue.
Was this the right choice? Or would simply using revenue be more appropriate?
Justify your answer. 10%
